---
title: "CellPhoneReviews"
author: "Harshitha Shabad"
date: "2/10/2020"
output: html_document
---

## Description

- "Cell Phone Reviews" Data set is taken from Kaggle. It has 50k rows and 11 columns.

- Kaggle link : https://www.kaggle.com/masaladata/14-million-cell-phone-reviews#phone_user_review_file_1.csv

- It contains user ratings and reviews for different brands of cell phones.

- Reviews given in english language only have been considered for this assignment.

- Below are the variables present in dataset:

  - phone_url: unique identifier of the cell phone
  - date : date when the review/rating was written
  - lang : language of the review
  - country : country where the review was written
  - source : publisher/website where the review was published
  - domain : website link to the publisher
  - scores : core/rating to the cell phone given by the user
  - score_max : maximum score/rating that the user can given
  - extract : brief review of the cell phone
  - author : name of the author who wrote the review
  - product : name/brand of the product

## Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
```

## Read CSV
```{r message=FALSE, warning=FALSE}
df <- read_csv(file="CellPhoneReviews.csv")
head(df, 3)
```

## Summary

- This data set contains only one nuemrical data column which is rating given to the cell phone on a maximum of 10.
- Score data is summarised to observe mean, median, quartiles, min, max etc

```{r message=FALSE, warning=FALSE}
summary(df[ ,"score"])
```


## Pre processing the dataset

Separated Date(year, Month, Date) to different columns,
stored data into new dataframe newdf, as this data is used for analysis by plotting graphs.


```{r message=FALSE, warning=FALSE}
newdf <- df %>%
  separate(date, into = c("Month", "Date", "Year"), sep = "/", convert = TRUE)
head(newdf, 3)

```
## Visualization1

- Score for phones plotted Year wise for each country
- The graph shows people in US gave more number of scores either low or high, People from other english speaking countries gave very less reviews

``` {r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
ggplot(data = newdf, mapping = aes(x = Year, y = score, color=country)) +
  geom_point()+
  theme_gdocs()+
  scale_color_gdocs()
```

## Visualization2

- product plotted against country.
- This will tell you which type of phone is getting review from which country.

``` {r message=FALSE, warning=FALSE}
ggplot(data = newdf, mapping = aes(x = product, y = country)) +
  geom_point()+
  theme_gdocs()+
  scale_color_gdocs()
```

## Visualization3

- phone_url is the unique identifier of the type of the cell phone plotted against score.
- This will tell you which type which phone has the highest score.
- From graph we can say that apple and samsung has high scores.

``` {r message=FALSE, warning=FALSE}
ggplot(data = newdf, aes(x = phone_url, y = score))+
  geom_bar(stat="identity")
```

## NLP

Tokenization
- Turn text to tokens

``` {r message=FALSE, warning=FALSE}
library(tidytext)
library(stringr)
library(tidyverse)
library(dplyr)

df = df %>%
mutate(extract = str_replace_all(extract, "(<br />)+", " ")) %>%
select(extract, score, score_max, date, lang, country,product)
df

tokens <- df %>%
unnest_tokens(output = word, input = extract)
tokens
```


Remove stopwords

``` {r message=FALSE, warning=FALSE}
sw = get_stopwords()
sw
cleaned_tokens <- tokens %>%
filter(!word %in% sw$word)
```

Remove Numbers

``` {r message=FALSE, warning=FALSE}
nums <- cleaned_tokens %>%
filter(str_detect(word, "^[0-9]")) %>%
select(word) %>% unique()
nums

cleaned_tokens <- cleaned_tokens %>%
filter(!word %in% nums$word)
```


Remove Rare Words

``` {r message=FALSE, warning=FALSE}
cleaned_tokens %>%
count(word, sort = T) %>%
rename(word_freq = n) %>%
ggplot(aes(x=word_freq)) +
geom_histogram(aes(y=..count..), color="black", fill="pink", alpha=0.3) +
scale_x_continuous(breaks=c(0:5,10,100,500,10e3), trans="log1p", expand=c(0,0)) +
scale_y_continuous(breaks=c(0,100,1000,5e3,10e3,5e4,10e4,4e4), expand=c(0,0)) +
theme_bw()
```

``` {r message=FALSE, warning=FALSE}

rare <- cleaned_tokens %>%
count(word) %>%
filter(n<10) %>%
select(word) %>% unique()
rare
```

``` {r message=FALSE, warning=FALSE}
cleaned_tokens <- cleaned_tokens %>%
filter(!word %in% rare$word)
length(unique(cleaned_tokens$word))
```

Word Cloud

``` {r message=FALSE, warning=FALSE}
library(wordcloud)
# define a nice color palette
pal <- brewer.pal(8,"Dark2")
# plot the 100 most common words
cleaned_tokens %>%
count(word) %>%
with(wordcloud(word, n, random.order = FALSE, max.words = 100, colors=pal))
```

- From the wordcloud we can say that most of the reviews are about iphone, samsung and about phone battery, screen, camera etc.
- We can also say that most of the words are positive.


Sentiment analysis

``` {r message=FALSE, warning=FALSE}
sent_reviews = cleaned_tokens %>%
left_join(get_sentiments("nrc")) %>%
rename(nrc = sentiment) %>%
left_join(get_sentiments("bing")) %>%
rename(bing = sentiment) %>%
left_join(get_sentiments("afinn")) %>%
rename(afinn = value)
sent_reviews
```

Most common positive and negative words

``` {r message=FALSE, warning=FALSE}
bing_word_counts <- sent_reviews %>%
filter(!is.na(bing)) %>%
count(word, bing, sort = TRUE)
bing_word_counts
```

``` {r message=FALSE, warning=FALSE}
bing_word_counts %>%
filter(n > 2000) %>%
mutate(n = ifelse(bing == "negative", -n, n)) %>%
mutate(word = reorder(word, n)) %>%
ggplot(aes(word, n, fill = bing)) +
geom_col() +
coord_flip() +
labs(y = "Contribution to sentiment")
```

- From above sentiment scores we can say that most of the words in the reviews are positive.
- There are very few words in the reviews which are negative.

